Handovers - SIPHER 7 Equivalent Income

### 2023-06-12 minos/validation/handovers_S7.Rmd
Expanded the handovers_S7 script with lots of additional validation plots

```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

@@

```{r}
start.year <- 2020

save.path <- '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/SIPHER7/Handovers/'
```

@@

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'S7_housing_quality',
                 save = TRUE,
                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
```

@@

```{r}
hous.pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_neighbourhood_safety')

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'S7_neighbourhood_safety',
                 save = FALSE,
                 save.path = '/home/luke/Documents/WORK/MINOS/VALIDATION_PLOTS/Cross-Validation/')
```

@@

>>>>

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

@@

```{r}
start.year <- 2020
save.path <- here::here("plots", "handovers", 'SIPHER7')
create.if.not.exists(save.path)

shall.we.save <- TRUE
```

@@

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'S7_housing_quality',
                 save = TRUE,
                 save.path = save.path)
```

@@

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_neighbourhood_safety')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_neighbourhood_safety',
                 save = FALSE,
                 save.path = save.path)
```

@@

## S7 Labour State

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')

lab.state <- prepped.list$var
lab.state.norm <- prepped.list$norm

# Now plot
ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Labour State') +
  xlab('Year') +
  ylab('Proportion')

ggsave(filename = 'S7_labour_state.png',
       plot = last_plot(),
       path = save.path)

rm(prepped.list, lab.state, lab.state.norm)
```

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_labour_state')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_labour_state',
                 save = FALSE,
                 save.path = save.path)
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_labour_state)
base.s <- base.dat %>%
  select(pidp, age, time, S7_labour_state)

spaghetti_plot(spag, 'S7_labour_state',
               save = TRUE,
               save.path = save.path)

## S7 Physical Health

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_physical_health')

var <- prepped.list$var
norm <- prepped.list$norm

tit <- 'S7 Physical Health'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = S7_physical_health, colour = S7_physical_health)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=S7_physical_health)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

ggsave(filename = 'S7_physical_health.png',
       plot = last_plot(),
       path = save.path)

rm(prepped.list, var, norm, tit)
```

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_physical_health')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_physical_health',
                 save = FALSE,
                 save.path = save.path)
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_physical_health)
base.s <- base.dat %>%
  select(pidp, age, time, S7_physical_health)

spaghetti_plot(spag, 'S7_physical_health',
               save = TRUE,
               save.path = save.path)

## S7 Mental Health

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_mental_health')

var <- prepped.list$var
norm <- prepped.list$norm

tit <- 'S7 Mental Health'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = S7_mental_health, colour = S7_mental_health)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=S7_mental_health)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

ggsave(filename = 'S7_mental_health.png',
       plot = last_plot(),
       path = save.path)

rm(prepped.list, var, norm, tit)
```

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_mental_health')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_mental_health',
                 save = FALSE,
                 save.path = save.path)
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, S7_mental_health)
base.s <- base.dat %>%
  select(pidp, age, time, S7_mental_health)

spaghetti_plot(spag, 'S7_mental_health',
               save = TRUE,
               save.path = save.path)
